Draft_Application_Stochastic_Volatility

### 2021-07-20 Real Dataset SV.Rmd
100000 particles update

```{r include=FALSE}
Errorcomp3<-matrix(NA,ncol=2,nrow=1,byrow=TRUE)
colnames(Errorcomp3)<-c("RMSE", "MAE")
rownames(Errorcomp3)<-("Discrepancy")
Errorcomp3[1,]<-c(0.04407704,0.01667898)

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(kableExtra)
kbl(Errorcomp3, align="c", longtable = T, booktabs = T, caption="Bootstrap vs Auxiliary PF, 50000 particles",digits=5)
```

@@

In section XX we compared such distributions already, pointing out three main behaviours, namely that of the SIS algorithm, that of the Liu and West particle filter and that of the remaining filters; however, we did not have metrics that could help us clearly point at one behaviour as the closest to reality. We will now use a realised volatility measure as one such metric.

>>>>

```{r include=FALSE}
Errorcomp3<-matrix(NA,ncol=2,nrow=2)
colnames(Errorcomp3)<-c("RMSE", "MAE")
rownames(Errorcomp3)<-c("N=50000", "N=100000")
Errorcomp3[1,]<-c(0.04407704,0.01667898)
Errorcomp3[2,]<-c(0.03575915,0.01476220)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results="asis"}
library(kableExtra)
kbl(Errorcomp3, align="c", longtable = T, booktabs = T, caption="Discrepancy between Bootstrap and Auxiliary PFs",digits=5)
```

@@

In section XX we compared several filtered distributions, pointing out three main behaviours, namely that of the SIS algorithm, that of the Liu and West particle filter and that of the remaining filters. However, we did not have metrics that could help us clearly point at one behaviour as the closest to reality. In this section, we will employ a realised volatility measure as one such metric.
